Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-05 ProbabilisticCoherence.tex
Cleaned up abstract

\begin{abstract}
  The process by which forecasts are adjusted to ensure coherence to aggregation constraints that hold for real data - known as forecast reconiliation - is extended from the point forecasts to probabilistic forecasts.  This is achieved by redefining many concepts from the existing literature in terms of linear mappings in general, and projections more specifically.  New theorems establish that linear reconciliation can recover the true predictive distribution in the elliptical case as well as general conditions for when this can be achieved via projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that  reconciliation via projection a) preserves unbiasedness and b) dominates unreconciled forecasts in a mean squared error sense.  Strategies for forecast evaluation based on scoring rules are discussed and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive disstribution coheres with aggregation constraints.  Finally evidence from simulation study show that reconciliation based on an oblique projection, derived from the MinT method of \cite{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
\end{abstract}

>>>>

\begin{abstract}
  Adjusting forecasts to ensure coherence with aggregation constraints that hold for real data - a process known as forecast reconiliation - is extended from point forecasts to probabilistic forecasts.  This is achieved by redefining forecast reconciliation in terms of linear mappings in general, and projections more specifically.  New theorems establish that the true predictive distribution can be recovered in the elliptical case by a linear mapping and general conditions are derived for when this linear mapping is a projection. A geometric interpretation is also used to prove two new theoretical results for point forecasting; that  reconciliation via projection a) preserves unbiasedness and b) dominates unreconciled forecasts in a mean squared error sense.  Strategies for forecast evaluation based on scoring rules are discussed and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive disstribution coheres with aggregation constraints.  Finally evidence from simulation study show that reconciliation based on an oblique projection, derived from the MinT method of \cite{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
\end{abstract}
